Staged Abstract Interpreters

### 2019-09-11 paper/60_cases.tex
polish

We show AC can be understood and implemented as an instance of staging abstract
interpreters. We first revisit the original implementation of abstract
compilation for 0-CFA, and then reproduce their result by simply adding stage
annotations.  The program generated by our approach provides approximately the
same improvement with regards to speed, but without changing a single line of
the analyzer program using type-based staging annotations. However, AC requires
more engineering effort, i.e., rewriting the whole analyzer into the
closure-generation form. Moreover, as shown in Section~\ref{staged_ds}, our
approach is able to not only remove the interpretive overhead, but also enable
several optimizations such as specialized data structures.

>>>>

We show that AC can be understood and implemented as an instance of staging abstract
interpreters. We first revisit the original implementation of abstract
compilation for 0-CFA, and then reproduce their result by simply adding stage
annotations.  The program generated by our approach provides approximately the
same improvement with regards to speed, but without changing a single line of
the analyzer program using type-based staging annotations. However, AC requires
more engineering efforts, i.e., rewriting the whole analyzer into the
closure-generation form. Moreover, as shown in Section~\ref{staged_ds}, our
approach is able to not only remove the interpretive overhead, but also enable
several optimizations such as specialized data structures.
